%!TEX root = ../luanvan.tex
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
Applying information technology to the management of diplomas and certificates has increased significantly in overall efficiency. The information management system helps the issuers, verifiers, the owners of diplomas and certificates in issuing, searching, verifying, and recognizing diplomas and certificates. At the same time, it ensures the confidentiality of the personal information of the diploma or certificate holders which is made public.

To ensure the privacy and confidentiality of the information and solve problems that exist when comparing information by hand, the research topic is the certificate management system based on blockchain technology. A Hyperledger Fabric blockchain network is used to deploy a proof of concept model that stores certificate information on the blockchain and then verifies it with limited disclosure of the owner’s information to the party that needs to verify.

In the model, the authentication of access rights is performed through a server. Thanks to Hyperledger Fabric's internal digital signatures, certificate information can be authenticated and trusted. The model’s interface is developed using a web platform so that users can easily use it. Based on the test results, the certificate management system meets the technical requirements including issuing certificates and verifying valid certificates through less personal information disclosure mechanism.
